A Comparison of Parallel Graph Processing Benchmarks

### 2017-02-17 papers/publication/paper-pollard.tex
conflict merges

Each experiment uses 32 roots per graph. As with the Graph500, each root is selected to have a degree greater than 1. In the case of PageRank, we simply run PageRank 32 times.

When possible, we measure the data set construction time as the time to translate from the unstructured file data in RAM to the graph representation on which the algorithm can be performed. This is not possible for PowerGraph and GraphBIG because they read in the input file and build a graph simultaneously. The Graph500 builds the graph once and performs the BFS on each root in turn, speeding up experimentation but only giving a single data point for the data set construction.

We plot many of the results as box plots with an implied 32 data points per box.

@@

We consider three algorithms: Breadth First Search (BFS), Single Source Shortest Paths (SSSP), and PageRank, though not all algorithms are implemented on all systems. We inspected the source code of the surveyed parallel graph processing systems to ensure the same phases of execution are measured across differing execution and programming paradigms.

@@

Overall, the GAP Benchmark Suite was the highest-performing system across the given datasets and the most scalable. However, this is only for relatively small graphs; all the graphs used here had at most $2^{22}$ vertices. It should be noted that GAP is also the most recent of projects. Thus, we recommend graph processing algorithm designers compare their implementations against the GAP Benchmark Suite as a good test of performance.

>>>>

Each experiment uses 32 roots per graph. As with the Graph500, each root is selected to have a degree greater than 1. For PageRank, we simply run the algorithm 32 times. We plot many of the results as box plots with an implied 32 data points per box.

When possible, we measure the dataset construction time as the time to translate from the unstructured file data in RAM to the graph representation on which the algorithm can be performed. This is not possible for PowerGraph and GraphBIG because they read in the input file and build a graph simultaneously. The Graph500 builds the graph once and performs the BFS on each root in turn, speeding up experimentation but only giving a single data point for the dataset construction.

@@

We consider three algorithms: Breadth First Search (BFS), Single Source Shortest Paths (SSSP), and PageRank, although not all algorithms are implemented on all systems. We inspected the source code of the surveyed parallel graph processing systems to ensure the same phases of execution are measured across differing execution and programming paradigms.

@@

Overall, the GAP Benchmark Suite was the highest-performing system across the given datasets but the least scalable. However, this is only for relatively small graphs; all the graphs used here had at most $2^{22}$ vertices. It should be noted that GAP is also the most recent of projects. Thus, we recommend graph processing algorithm designers compare their implementations against the GAP Benchmark Suite as a good test of performance.

We found Graphmat to not be highly performant but relatively scalable. One explanation is GraphMat's underlying computation model (sparse matrix operations) paired the increased overhead of GraphMat's doubly-compressed sparse row (DSCR) graph representation is more conducive to larger-scale graphs.
% Furthermore, sparse matrix operations have been well studied so achieving good scalability is more realistic [cite]
